pema application

### 2022-12-05 paper/manuscript.Rmd
fixed typo

The regularized horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
the regularized horseshoe prior is given by:
\begin{align}
\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with}\\ (\#eq:hs)
\tilde{\tau}_j^2 &= \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
\lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
\tau_j &\sim \text{student-}t^+(\nu_2, 0, 1)\\
c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
\end{align}
Note that global shrinkage parameters, which are not subscripted, affect all regression coefficients.
Local parameters are indicated by subscript $_j$, and affect each individual regression coefficient separately.
In these equations, $N$ denotes the normal distribution,
student-$t^+$ denotes the positive half of a t distribution,
and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
where larger values for the global scale parameter $\lambda^2_0$ widen the rande of values covered by the priors.
The global degrees of freedom $\nu_1$ control the overall thickness of the tails,
with higher values resulting in thinner tails, which assigning less probability mass to extreme values.
Lighter tails can aid model convergence when the model is weakly identified; for example, when there are more moderators than observations.
The prior $\tau_j$ controls the local shrinkage of specific regression coefficients;
its scale is fixed, but its degrees of freedom $\nu_2$ control the incidence of extreme values in a similar way as $\nu_1$.
A finite "slab" applies additional regularization to very large coefficients,
which provides greater numerical stability of the model.
This slab is governed by a degrees of freedom parameter $\nu_3$ and a scale parameter $s$.
As before, increasing $\nu_3$ assigns less probability mass to extreme values.
Increasing $s$ increases the range of values covered by the slab.

>>>>

The regularized horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
the regularized horseshoe prior is given by:
\begin{align}
\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with}\\ (\#eq:hs)
\tilde{\tau}_j^2 &= \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
\lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
\tau_j &\sim \text{student-}t^+(\nu_2, 0, 1)\\
c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
\end{align}
Note that global shrinkage parameters, which are not subscripted, affect all regression coefficients.
Local parameters are indicated by subscript $_j$, and affect each individual regression coefficient separately.
In these equations, $N$ denotes the normal distribution,
student-$t^+$ denotes the positive half of a t distribution,
and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
where larger values for the global scale parameter $\lambda^2_0$ widen the range of values covered by the priors.
The global degrees of freedom $\nu_1$ control the overall thickness of the tails,
with higher values resulting in thinner tails, which assigning less probability mass to extreme values.
Lighter tails can aid model convergence when the model is weakly identified; for example, when there are more moderators than observations.
The prior $\tau_j$ controls the local shrinkage of specific regression coefficients;
its scale is fixed, but its degrees of freedom $\nu_2$ control the incidence of extreme values in a similar way as $\nu_1$.
A finite "slab" applies additional regularization to very large coefficients,
which provides greater numerical stability of the model.
This slab is governed by a degrees of freedom parameter $\nu_3$ and a scale parameter $s$.
As before, increasing $\nu_3$ assigns less probability mass to extreme values.
Increasing $s$ increases the range of values covered by the slab.
